\TESS Photometric Mapping of a Terrestrial Planet in the Habitable Zone: Detection of Clouds, Oceans, and Continents

### 2019-03-24 tex/ms.tex
working on the ms

% Title
\title{\TESS Photometric Mapping of Surface Features on a Habitable-Zone Terrestrial Planet: Clouds, Oceans, and Continents}
%\title{Detection of Continents on a Habitable-Zone Terrestrial Planet with \TESS}

@@

\begin{abstract}
\todo{[maybe change first sentences to focus on planet mapping \& give the game away less?]}
The Transiting Exoplanet Survey Satellite (\TESS) mission is a targeted effort to detect planets smaller than Neptune around bright, nearby stars. 
While \TESS is already enjoying great success with the discovery of many new worlds, the strongest signal in its data is typically ignored, as it lurks in the background of every camera pixel. 
In this work, we extract this signal and demonstrate that it is consistent with a terrestrial planet with a rotation period of 1 day. 
Using a spherical harmonic-based reflection model developed as an extension of the STARRY package, we are able to reconstruct the surface features of this rocky world. 
We recover a time-variable albedo map of the planet including persistent regions which we interpret as continental features and cloud banks. 
We argue that this planet represents the most promising detection of a habitable world to date, although the potential intelligence of any life on it is yet to be determined.
\end{abstract}

@@

%Resolving the features of planetary atmospheres and surfaces with precise photometry is a crucial 
Precise photometry obtained over long periods of time can reveal the atmospheric and surface features of an exoplanet through the method known as phase mapping. \todo{(literature background \& citations)}

@@

In this work, we build on this methodological foundation to perform reflected-light mapping of planetary surface features on Sol d. 
We give an overview of the \TESS data used in Section \ref{sec:data}. 
In Section \ref{sec:methods}, we describe the methods employed to infer a map from these data, including the adaptation of the STARRY algorithm to reflection mapping, the modeling of spacecraft-related systematics, and the likelihood and priors used. 
We present results in Section \ref{sec:results} and make comparison of these findings to state-of-the-art terrestrial planet maps from the literature in Section \ref{sec:discussion}. 
Finally, we conclude in Section \ref{sec:conclusion} with a look at future prospects for phase-curve mapping of terrestrial exoplanets.

@@

\subsection{Reflected-Light Mapping with STARRY}

\todo{(brief recap of STARRY)}

\todo{(adapting STARRY to reflected light/variable illumination phase - possibly make the gritty math details be an appendix?)}

@@

@@

\acknowledgements{\todo{(Artist acknowledgement)} The authors gratefully acknowledge Dan Foreman-Mackey, David W Hogg, Ben Pope, \todo{and ...} for useful conversations. Crucial parts of this work were carried out at the TESS Data Workshop, hosted by Space Telescope Science Institute, and the Building Early Science with TESS Workshop, hosted by the University of Chicago.}
\facility{TESS}
\software{Astropy, Matplotlib, Numpy, STARRY \citep{Luger2019}, TensorFlow}
% Bibliography
\pagebreak
\bibliography{bib}

>>>>

% Title
\title{\TESS Photometric Mapping of a Terrestrial Planet in the Habitable Zone: 
       Detection of Clouds, Oceans, and Continents}
%\title{Detection of Continents on a Habitable-Zone Terrestrial Planet with \TESS}

@@

\begin{abstract}
\todo{[maybe change first sentences to focus on planet mapping \& give the game 
away less?]} The Transiting Exoplanet Survey Satellite (\TESS) mission is a 
targeted effort to detect planets smaller than Neptune around bright, nearby stars. 
While \TESS is already enjoying great success with the discovery of many new worlds, 
the strongest signal in its data is typically ignored, as it lurks in the background 
of every camera pixel. In this work, we extract this signal and demonstrate that 
it is consistent with a terrestrial planet with a rotation period of 1 day. 
Using a spherical harmonic-based reflection model developed as an extension of 
the \starry package, we are able to reconstruct the surface features of this rocky 
world. We recover a time-variable albedo map of the planet including persistent 
regions which we interpret as continental features and cloud banks. 
We argue that this planet represents the most promising detection of a habitable 
world to date, although the potential intelligence of any life on it is yet to 
be determined.
\end{abstract}

@@

%Resolving the features of planetary atmospheres and surfaces with precise 
%photometry is a crucial 
Precise photometry obtained over long periods of time can reveal the atmospheric 
and surface features of an exoplanet through the method known as phase mapping. 
\todo{(literature background \& citations)}

@@

In this work, we build on this methodological foundation to perform 
reflected-light mapping of planetary surface features on Sol d. 
We give an overview of the \TESS data used in Section \ref{sec:data}. 
In Section \ref{sec:methods}, we describe the methods employed to infer a map 
from these data, including the adaptation of the \starry algorithm to reflection 
mapping, the modeling of spacecraft-related systematics, and the likelihood and 
priors used. 
We present results in Section \ref{sec:results} and make comparison of these 
findings to state-of-the-art terrestrial planet maps from the literature in 
Section \ref{sec:discussion}. 
Finally, we conclude in Section \ref{sec:conclusion} with a look at future 
prospects for phase-curve mapping of terrestrial exoplanets.

@@

\subsection{Reflected-Light Mapping with \starry}

\todo{(brief recap of \starry)}

\todo{(adapting \starry to reflected light/variable illumination phase - 
possibly make the gritty math details be an appendix?)}

@@

\begin{figure}[t!]
    \begin{centering}
    \includegraphics[width=\linewidth]{figures/phases.pdf}
    \caption{\label{fig:phases}
             \tess view of Sol d on every date in Sectors 1
             and 2 that was included in the regression. Each image is
             labeled with the corresponding timestamp in TJD.
             \codelink{EarthView}
             }
    \end{centering}
\end{figure}

@@

\acknowledgements{\todo{(Artist acknowledgement)} The authors gratefully 
acknowledge Dan Foreman-Mackey, David W Hogg, Ben Pope, \todo{and ...} 
for useful conversations. Crucial parts of this work were carried out at the 
TESS Data Workshop, hosted by Space Telescope Science Institute, and the 
Building Early Science with TESS Workshop, hosted by the University of Chicago.}
\facility{TESS}
\software{Astropy, Matplotlib, Numpy, \starry \citep{Luger2019}, TensorFlow}
% Bibliography
\pagebreak
\bibliography{bib}
